---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

## Bus Trip Observations

This dynamic report summarises observational logging data collected from bus trips.

```{r import-data}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ_2ZHK55mzQyTotFrfOHVDtVrNOUGny5iW8jE4-9b-pf9pXVBUljsz9vySqCvbD02RGtB-EpMm-Imk/pub?output=csv")

latest_data <- logged_data |>
  rename(
    time_of_day = `What time of day was this bus trip?`,
    passengers = `Approximately how many passengers were on the bus when you observed it?`,
    seat_available = `Was there an empty seat available when you got on the bus?`,
    trip_minutes = `About how many minutes did this bus trip take?`,
    crowding = `How crowded did the bus feel overall?`
  ) |>
  mutate(
    passengers = as.numeric(passengers),
    trip_minutes = as.numeric(trip_minutes)
  )
```

```{r summary-values}
num_trips <- nrow(latest_data)
avg_passengers <- mean(latest_data$passengers, na.rm=TRUE)
avg_minutes <- mean(latest_data$trip_minutes, na.rm=TRUE)
max_passengers <- max(latest_data$passengers, na.rm=TRUE)
```

A total of `r num_trips` bus trips have been recorded so far.

The average number of passengers observed per trip is `r round(avg_passengers, 1)`.

The average trip duration is `r round(avg_minutes, 1)` minutes.

The highest number of passengers observed on a single trip was `r max_passengers`.

## Bar chart 1

```{r bar-chart-1}
ggplot(latest_data, aes(x=time_of_day)) +
  geom_bar() +
  labs(
    title = "Number of Bus Trip Observations by Time of Day",
    x = "Time of day",
    y = "Count"
  )
```

## Bar chart 2

```{r bar-chart-2}
ggplot(latest_data, aes(x=crowding)) +
  geom_bar() +
  labs(
    title = "Crowding Level of Observed Bus Trips",
    x = "Crowding level",
    y = "Count"
  )
```
